Patient-Specific Neural Field Model

### 2010-07-12 ltx/data_paper/DataPaper.tex
added temporal freq figure
added spatial freq cross-section and field observation figures

\begin{abstract}
	\begin{itemize}
		\item Background
		\item Method
		\item Result
		\item Conclusion
	\end{itemize}
\end{abstract}

@@

\subsection{Data Collection}
\begin{itemize}
	\item Show medical imaging
	\item Show LFP Data (background, seizure, post-seizure)
	\item Show spectral properties of LFPs
\end{itemize}
\begin{figure}[!ht]
\begin{center}
\includegraphics{./Figures/LFPs.eps}
\end{center}
\caption{{\bf Local Field Potentials}. Data recorded from the first five channels of the array. The red dotted line indicates the seizure onset and the blue dashed line indicates the seizure end.}
\label{fig:SpatialFreqObservation}
\end{figure}

@@

>>>>

\begin{abstract}

	\begin{itemize}
		\item Background
		\item Method
		\item Result
		\item Conclusion
	\end{itemize}
\end{abstract}

@@

\subsection{Data Collection}
\begin{itemize}
	\item Show medical imaging
	\item Show LFP Data (background, seizure, post-seizure)
	\item Show spectral properties of LFPs
\end{itemize}

\begin{figure}[!ht]
\begin{center}
\includegraphics{./Figures/LFPs.eps}
\end{center}
\caption{{\bf Local Field Potentials}. Data recorded from the first five channels of the array. The red dotted line indicates the seizure onset and the blue dashed line indicates the seizure end.}
\label{fig:TimeSeries}
\end{figure}

\begin{figure}[!ht]
\begin{center}
\includegraphics{./Figures/FieldObservations.eps}
\end{center}
\caption{{\bf Snap-shots of the spatial aspects of the observed field}. The snap-shots are ordered from A to I forming a consecutive sequence spaced 2.5~ms apart starting at 34.024s}
\label{fig:FieldObserations}
\end{figure}

\begin{figure}[!ht]
\begin{center}
\includegraphics{./Figures/TemporalFreq.eps}
\end{center}
\caption{{\bf Spectra from local field potential recordings}. A. Pre-seizure observations. B. Seizure observations. C. Post-seizure observations.}
\label{fig:TemporalFreqObservation}
\end{figure}

@@

\begin{figure}[!ht]
\begin{center}
\includegraphics{./Figures/SpatialFreqCrossSection.eps}
\end{center}
\caption{{\bf Diagonal cross-section of the spatial frequency plots of the observed neural field}. A. Pre-seizure observations. B. Seizure observations. C. Post-seizure observations.}
\label{fig:SpatialFreqObservation}
\end{figure}
